---
title: "WeighIt Corporation- Assignment 3"
author: "Vamshee Deepak Goud Katta"
date: "10/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Weigelt Production

## Reading the objective fn and constraints from lp file

```{r}
library(lpSolveAPI)

lprec <- read.lp("vkatta_3.lp")

lp.control(lprec,sense='max')

```

## Arranging the values in table with constraints against products

```{r}

RowNames <- c("P1cap", "P2cap", "P3cap", "P1space", "P2space", "P3space", "LSales", "MSales", "SSales", "P1-P2", "P1-P3")
ColNames <- c("Large1", "Medium1", "Small1", "Large2", "Medium2", "Small2", "Large3", "Medium3", "Small3")
dimnames(lprec) <- list(RowNames, ColNames)

```

## Solving the LP problem using the Solve() function

```{r}

solve(lprec)

get.objective(lprec)

get.variables(lprec)

get.constraints(lprec)

```

## Arranging the solution of the LP problem with variables against values

```{r}

solution <- data.frame(ColNames, get.variables(lprec)) # Solution of the problem 
colnames(solution) <- c("variable", "value")
solution

```

## Finding shadow prices and reduced cost of the solved LP problem

```{r}

get.sensitivity.rhs(lprec) # Shadow Prices

get.sensitivity.obj(lprec) # Reduced Cost

```

## Reading Objective fn and Constraints from lp file

```{r}

lprec.dual <- read.lp("vkatta_3.dual.lp")

lp.control(lprec,sense='min')
set.bounds(lprec.dual, lower = c(0,0,0,0,0,0,0,0,0,-Inf,-Inf), upper = rep(Inf,11))
  
```

## Solving Dual of the LP problem

```{r}

solve(lprec.dual)

get.objective(lprec.dual)

get.variables(lprec.dual)

get.constraints(lprec.dual)

```

