---
title: "vkatta_4"
author: "Vamshee Deepak Goud Katta"
date: "10/25/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Heart Start AEDs

## Reading LP file

```{r}

library(lpSolve)
library(lpSolveAPI)
lprec <- read.lp("vkatta_4.lp")

```

## Solving the LP problem using the Solve() function

```{r}

solve(lprec)

get.objective(lprec)

get.variables(lprec)

get.constraints(lprec)

```

## Arranging the solution of the LP problem with variables against values

```{r}

ColNames <- c("AW1", "AW2", "AW3", "BW1", "BW2", "BW3")
solution <- data.frame(ColNames, get.variables(lprec)) # Solution of the problem 
colnames(solution) <- c("variable", "value")
solution

```

## Hence, Plant A is to produce 100 units and ship 60 units to Warehouse2 and 40 units to Warehouse3
## Plant B is to produce 110 units and ship 80 units to Warehouse1 and 30 units to Warehouse3

# 2. Texxon Oil Distribution

## 1) Minimum Cost of providing oil to refineries

## Given,  

### Capacity of wells W1, W2 and W3 are 93, 88 and 95 respectively
### Requirements of refineries R1, R2, R3, R4, R5 are 30, 57, 48, 91 and 48 respectively
        
## Let,
      Xij be the flow of oil from well i to Pump j
      where, i= W1, W2, W3 and j= A, B, C
      
      Yij be the flow of oil from Pump i to Refinery j
      where, i= A, B, C and j= R1, R2, R3, R4, R5
      
## Charges levied on pipeline usage are as follows:
AW1 - Well1 to PumpA = 1.52       
AW2 - Well2 to PumpA = 1.70       
AW3 - Well3 to PumpA = 1.45       
BW1 - Well1 to PumpB = 1.60       
BW2 - Well2 to PumpB = 1.63       
BW3 - Well3 to PumpB = 1.57       
CW1 - Well1 to PumpC = 1.40       
CW2 - Well2 to PumpC = 1.55       
CW3 - Well3 to PumpC = 1.30       
AR1 - PumpA to Refinery1 = 5.15       
BR1 - PumpB to Refinery1 = 5.12       
CR1 - PumpB to Refinery1 = 5.32       
AR2 - PumpA to Refinery2 = 5.69       
BR2 - PumpB to Refinery2 = 5.47       
CR2 - PumpC to Refinery2 = 6.16       
AR3 - PumpA to Refinery3 = 6.13       
BR3 - PumpB to Refinery3 = 6.05       
CR3 - PumpC to Refinery3 = 6.25       
AR4 - PumpA to Refinery4 = 5.63       
BR4 - PumpB to Refinery4 = 6.12       
CR4 - PumpC to Refinery4 = 6.17       
AR5 - PumpA to Refinery5 = 5.80       
BR5 - PumpB to Refinery5 = 5.71       
CR5 - PumpC to Refinery5 = 5.87
      
## Here, the minimum cost function is:
Min : 1.52AW1+ 1.70AW2+ 1.45AW3+ 1.60BW1+ 1.63BW2+ 1.57BW3+ 1.40CW1+ 1.55CW2+ 1.30CW3+ 5.15AR1+ 5.12BR1+ 5.32CR1+ 5.69AR2+ 5.47BR2+ 6.16CR2+
6.13AR3+ 6.05BR3+ 6.25CR3+ 5.63AR4+ 6.12BR4+ 6.17CR4+ 5.80AR5+ 5.71BR5+ 5.87CR5
      
## Where,
AW1 + BW1 + CW1 <= 93       
AW2 + BW2 + CW2 <= 88       
AW3 + BW3 + CW3 <= 95       
AR1 + BR1 + CR1 = 30        
AR2 + BR2 + CR2 = 57        
AR3 + BR3 + CR3 = 48        
AR4 + BR4 + CR4 = 91        
AR5 + BR5 + CR5 = 48

### Here, wells 1 and 3 are used to their capacity